%-------------------------------------------------------------------------------
% File:		Homework.tex
% Author:	Igor Janjic, Brian Hilnbrand, Danny Duangphachanh, Leah
%		Krynitsky  
% Description:	[ECE 4534] Embedded Systems Design
%		Background Research Assignment
%%------------------------------------------------------------------------------ 

%\documentclass{Book}

\input{./Preamble.tex}
\input{./Definitions.tex}
\input{./Programming.tex}

\begin{document}

\input{./Title.tex}

\subsection*{Background}
Of the first autonomous robots, none are more famous than Grey Walter's tortoises Elmer and Elsie. These two robots were very simple analog circuits equipped with three wheels for locomotion and light sensors which they used to navigate their environment and move toward illuminated recharging stations when low on power \cite{Walter:1950}. Since then, the design of autonomous robots has shifted toward the processing of sensory data using algorithms based in terms of digital computation. The remaining paper focuses on this last view of autonomous robotics.

\subsection*{Robot Framework Considerations}
The three primitives of robotics: plan, sense, act, as well as their relationships imply a robotic framework. Since the design specifications and hardware limitations are given, the robotics framework must then be determined by judging each framework's strengths and weaknesses as well as the compatibility between the framework and the choice of available sensors (described later). Thus, we are purposefully limiting our discussion to only those frameworks that coincide with usability of the various sensors available.

The framework must be able to handle quickly processing large amounts of complex information.

Additionally, the framework must be able to handle the prioritization of tasks. Since the robot has multiple goals that it is trying to achieve, often at the same time and often contradictory to each other, the control system framework must be able to rank goals by priority and focus computational power to solving high-priority goals first while at the same time reserving enough computational power to service low-priority goals.

The more sensors the robot has, the more information it is able to gather and then process to help it achieve its goals. The framework must be able to handle error in the sensors, overlapping sensors, inconsistent or failed sensors, and the addition of more sensors, 

\subsection*{Layered Control Paradigm \cite{Brooks:1985}}
This paradigm was designed by Brooks, R. At the MIT Artificial Intelligence Laboratory, which allowed for the design of various levels of intelligence in autonomous robots by building the control system in layers. Each layer is composed of simple computational modules communicating over low bandwidth channels asynchronously. The problem formulated in the language of control theory is as follows: a group of sensors receive information about the environment which the control system processes, turns into commands, and then sends to the motor controller which moves the robot accordingly.

\subsubsection*{Hierarchical/Deliberative Paradigm}
\subsubsection*{The Reactive Paradigm}
\subsubsection*{Hybrid Deliberate/Reactive Paradigm}
\subsubsection*{Automatic Planning}

\subsection*{Choice of Sensors}

\subsection*{Comparison of Algorithms}

\subsection*{Communication Protocols}
In general terms, a message intended for communication between two devices (the protocol) is comprised of two main parts: the header and the payload. The header consists of information about the message, including source or destination id, the nature of the message, and the size of the payload. The payload is the data which is being sent from one device to another. This payload can be formatted in any way, as long as it is consistent in both the source and destination.

Google Protocol Buffers \cite{Google:2014} are used in the automotive industry to format and serialize both small and large packets of information, preparing the payload for transmission to any destination. Once recieved at the destination, the payload can be deserialized and treated as an object, pulling specific pieces of data out of the payload as necessary. A single .proto file is written to define any number of different payloads to send, which is compiled by the protocol buffer compiler to produce libraries to be used for serialization. This provides an easy way to create payloads with lots of information if necessary, which can be created and understood seemlessly by both the source device and the destination device.

In addition, a modified transmission protocol \cite{NSI:2014} should be used to define the order and confirmation of transmission. If the link between two devices is thought of as an open stream of communication, it is wise to set up a series of handshakes and data packets to ensure correct communication. For example, one may want to send the header first to alert the destination device of an incomming payload, what information it will contain, and how long the stream of data is. Once the destination device has processed this header and is ready to recieve information from the source, such as a sensor data point, it will send a handshake, or similar confirmation. Since the destination device already knows the length of the incomming payload, there is no need to analyze it as it is comming in to catch a delimiter and end reception of a certain transmission.

On the other hand, delimeters are usefull when sending data that will always be in the same format every time, but of varying length. This removes the need for certain information to be sent ahead of time, such as payload type and length, and any other overhead the payload may contain. This could reduce the size of the transmission, making for a faster exchange.

\bibliographystyle{plain}
\bibliography{Biblio}

\end{document}

